##Analysis Process
*Data Clearing
*K-fold CV for different model
*Predict the class from testing data
##Data Clearing
========================================================
*Load these data and packages
```{r}
setwd("D:/Practical Machine Learning/Project_data")
ini.training = read.csv("pml-training.csv")[,-1]
ini.testing = read.csv("pml-testing.csv")[,-1]
library(caret);library(ggplot2)
```

*remove the column of all element are NA or NULL
```{r}
names(ini.training)
num.yes = length(which(ini.training$new_window == "yes"))
training = ini.training[,colSums(is.na(ini.training)) < (nrow(ini.training)-num.yes)]
ttt = which(ini.training$new_window == "yes")
ttry = training[-ttt,]
dd = which(sapply(ttry,class) == "factor")[-c(1,2,3,37)]

f.training = training[,-as.vector(dd)]
f.testing = ini.testing[,names(ini.testing) %in% names(f.training)[-59]]
f.testing$problem_id = ini.testing$problem_id
```

##K-fold CV for different model
*Creating a function to build different model for CV
```{r}
To.test.model = function(f.training,fold,model,...) {
  folds = createFolds(y = f.training$classe, k = fold,list = T, returnTrain =T)
  acc = vector()
  
  if (model == "nb") {is.pca ="pca"
  } else is.pca = NULL
  
  for(i in 1:fold) {
    mode_train = f.training[folds[[i]],]
    mode_test = f.training[-folds[[i]],]
    #browser()
    mod= train(classe~.,data=mode_train,method=model,preProcess = is.pca,verbose=...)
    confuesM = confusionMatrix(mode_test$classe,predict(mod,newdata = mode_test))
    acc[i] = confuesM$overall[1]
  }
  acc.aver = mean(acc)
  list("acc.obs"=acc,"acc.mean"=acc.aver)
}
```

*Because I have no much time...so I reduce the sample and cv times
```{r}
f.training = f.training[sample(1:nrow(f.training),1500),]
```

*Naive Byaes & PCA
```{r}
set.seed(7)
nb.time = Sys.time()
NB_PCA = To.test.model(f.training=f.training,fold=3,model="nb")
exe.time_nb = Sys.time()-nb.time
```

*boosting
```{r}
set.seed(7)
bo.time = Sys.time()
boot_tree = To.test.model(f.training = f.training ,fold=3,model="gbm",verbose=F)
exe.time_bo = Sys.time()-bo.time
```

*Random Foreast
```{r}
set.seed(7)
rf.time = Sys.time()
rf = To.test.model(f.training = f.training ,fold=3,model="rf")
exe.time_rf = Sys.time()-rf.time
```

*MARS
```{r}
set.seed(7)
mar.time = Sys.time()
mars = To.test.model(f.training = f.training ,fold=3,model="earth")
exe.time_mar = Sys.time()-mar.time
```

*Choic the best model:According to the accurace of average & variation, choice the best mode is boosting
```{r}
acc.da = data.frame(c(NB_PCA$acc.obs,boot_tree$acc.obs,rf$acc.obs),
                    rep(c("NB","Boosting","RF"),each=3)) 
colnames(acc.da) = c("Accuracy","Method")
p <- ggplot(acc.da, aes(factor(Method), Accuracy))
p + geom_boxplot()
c(sd(NB_PCA$acc.obs),sd(boot_tree$acc.obs),sd(rf$acc.obs))
```

```{r}
bestMod = traing(clases~.,data=f.training,method="gbm")
predict(bestMod,newdata=f.testing)
```








